\tool: Revisiting BadUSB with Type-C

### 2021-03-10 WOOT/Files/background.tex

%\noindent\outline{USB3.x}\\
\ac{USB} 3.0~\cite{usb30} was announced in 2008, with a super speed (5 Gbit/s) data
transfer rate. Like its predecessor, more classes of peripherals were supported
in this revision. In 2013, the \ac{USB} Type-C connector standard was introduced as a
part of \ac{USB} 3.1~\cite{usb31}, providing a unified connector type for
PowerDelivery, Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
security was introduced in 3.x revisions, meaning any device claiming
itself as a monitor can capture the video stream from the host. Exposing
such a multi-propose connector unprotected is insecure and allows attacks like
this work \tool. In 2017, \ac{USB} 3.2~\cite{usb32} was released, doubling the data
transfer rate (20 Gbit/s).

@@

As illustrated in Figure~\ref{fig:usb_conn}, the original \ac{USB} 1.x \& 2.x
connector only has two pins for data transferring \mbox{(D+ \& D-)}, which has
significantly limited data transfer rate \mbox{(5 Gbits/s Max)} and cannot support for
peripherals like DisplayPort \mbox{(10.8 Gbit/s Min)}. Apart from that, support for
other peripherals also require dedicated transferring lane as their standards
are not compatible with \ac{USB} in most cases.

@@

Thus, to provide support towards a wider range of peripherals, a 24-pins
standard called \ac{USB} Type-C~\cite{typec} is introduced in 2013 by \ac{USB}-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
pins is halved. Nevertheless, this standard has largely enhanced the capability
of the \ac{USB} 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
two high-speed data lanes \mbox{(TRX1 \& TRX2)} and kept the original data lane \mbox{(D+ \&
D-)}. The added lanes are used exclusively to support peripherals like
DisplayPort while the kept data lane transfers \ac{USB} packets.

%\noindent\outline{Security Problem}\\
During the development of \ac{USB} specification, security was considered insufficiently~\cite{sok}. As
the \ac{USB}-IF believes it is the duty of \acp{OEM}
to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
BadUSB~\cite{rubber} and our \tool.

>>>>

%\noindent\outline{USB3.x}\\
\ac{USB} 3.0~\cite{usb30} was introduced in 2008, with a super speed (5 Gbit/s) data
transfer rate. Like its predecessor, more classes of peripherals were supported
in this revision. In 2013, the \ac{USB} Type-C connector standard was introduced as a
part of \ac{USB} 3.1~\cite{usb31}, providing a unified connector type for
PowerDelivery, Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
security was introduced in 3.x revisions, meaning any device claiming
itself as a monitor can capture the video stream from the host. Exposing
such a multi-purpose connector unprotected is insecure and allows attacks similar to \tool. In 2017, \ac{USB} 3.2~\cite{usb32} was released, doubling the data
transfer rate (20 Gbit/s).

@@

As illustrated in Figure~\ref{fig:usb_conn}, the original \ac{USB} 1.x \& 2.x
connector only has two pins for data transferring \mbox{(D+ \& D-)}, which has
significantly limited data transfer rate \mbox{(5 Gbits/s Max)} and cannot support
peripherals like DisplayPort \mbox{(10.8 Gbit/s Min)}. Apart from that, support for
other peripherals also requires dedicated transferring lanes as their standards
are not compatible with \ac{USB} in most cases.

@@

Thus, to provide support towards a wider range of peripherals, a 24-pins
standard called \ac{USB} Type-C~\cite{typec} was introduced in 2013 by \ac{USB}-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
pins is halved. Nevertheless, this standard has largely enhanced the capability
of the \ac{USB} 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
two high-speed data lanes \mbox{(TRX1 \& TRX2)} and kept the original data lane \mbox{(D+ \&
D-)}. The added lanes are used exclusively to support peripherals like
DisplayPort while the kept data lane transfers \ac{USB} packets.

%\noindent\outline{Security Problem}\\
During the development of \ac{USB} specification, security was insufficiently considered~\cite{sok}. But \shuqing{but?}
the \ac{USB}-IF believes it is the duty of \acp{OEM}
to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
BadUSB~\cite{rubber} and our \tool.

### 2021-03-10 WOOT/Files/conclusion.tex
free conclusion from GoodUSB

Leveraging the new features of \ac{USB} 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The full control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes and shows it can
bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

@@

Responsible disclosure have already been carried out, we have already contacted Huawei and Apple through proper channel and are waiting for mitigation being deployed. By now, we have already heard from Huawei PSIRT who has already been analyzing this security issue while Apple has not responded yet.

>>>>

Leveraging the new features of \ac{USB} 3.x~\cite{usb30,usb31,usb32}, we explore a
new attack scheme named \tool and three attack modes. Each of these three modes
has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
victim's sensitive information in a stealthy way. The full control mode
archives the complete hijack of the target device, allowing us to perform various
types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
and PCs, we further test its ability under different modes. In our user study, we
obtain and analyze video stream extracted from 10 participants with \tool,
which demonstrates its capability in a real-life scenario. In the end, we
propose a new defense scheme named \textit{isolated UI rendering}, which can
effectively stop our \tool.

@@

Responsible disclosure have already been carried out, we have already contacted Huawei and Apple through proper channel and are waiting for mitigation being deployed. We revived response from Huawei on \nth{7} March and discussed about the mitigation plan on \nth{10} March while Apple has not responded yet.

### 2021-03-10 WOOT/Files/experiment.tex

\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
%\fengwei{I think it is necessary to explain them in the text again.}

@@

\subsection{Attack Initialization}
After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
\begin{itemize}
	\item \textbf{Screen Mirror}:
		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default. In this case, \tool will inject a sequence of keystrokes and mouse movements to set the victim's device into mirror their screen. For example, in Windows 10, \tool can inject `Win+P' keystroke and a mouse click on the `Duplicate' option. However, as \tool is unable to obtain the screen during this process, this can only be performed blindly with a possibility of failure.
	\item \textbf{Dismiss Notification}:
		In our experiment, we found that some devices will notify the user presence of an external screen. During our experiment, the following notifications are raised: 
		\begin{itemize}
		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen. 
		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
		 \item On iPad Pro (\nth{3} generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
		\end{itemize}
		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movement to dismiss some of these notifications. For example, in the first case, \tool is able to inject a sequence of mouse movement to set the screen at mirror mode to dismiss the pop-up.
\end{itemize}
\begin{comment}
\begin{table*}[]
	\begin{tabular}{|c|c|c|c|}
		\hline
		Device                                                               & Operating System                                                                                         & Notification              & Dismiss Action                                            \\ \hline
		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline
		\multirow{2}{*}{HUAWEI P30 (ELE-AL00)}                               & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}EMUI 11.0.0.135(C00E128R2P5)\\ Android 10 based\end{tabular}} & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Persistent notifications  & N/A                                                       \\ \hline
		\multirow{2}{*}{iPad Pro (3rd generation)}                           & \multirow{2}{*}{iOS 14.4 (Build 18D52)}                                                                  & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Pop-up (only when locked) & N/A                                                       \\ \hline
	\end{tabular}
	\linebreak
	\caption{Notifications about \tool}
	\label{tab:notification}
\end{table*}
\end{comment}

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10 (OS Build 18363.1379) with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raise a pop-up window asking victim's what mode should new screen be set to. \tool immediately inject a sequence of mouse movement and click to set itself as a mirror to the primary monitor. Thus we have successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attacker real-time feedback which allows attacker to perform more accurate attack.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

\textbf{Sharing Power Bank}.  Sharing power bank provides users with short-term
rental of power banks.  The company deploys power bank stations in the city and
users can rent a power bank from any of the power bank stations, charge their
device on the trip, return the rented power bank to the near stations, and pay
the rental fee.

@@

Not only does sharing power bank provides convenience to users, but it also
brings security issues.  We noticed that most of the power bank stations do not
check the integrity of power banks during the rental process, and users are
hardly cautious to check the power banks when connecting their devices.  An
attacker is able to tamper rented power banks and return them to a power bank
station causing a potential threat to subsequent users.

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that is popular in Asia. Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code paymeinformation from the video stream.  When the victim viewed text or photos withnt is typically performed in the following steps:
\ding{182} The client presents the payment QR code on the mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
By presenting this QR code, the client authorizes the proceeding transaction.
\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

Next, we explain one type of payments called micropayment. A micropayment is pre-determined by the payment
service provider with thresholds in the user agreement. In real-world scenarios, payment service providers use different rules
for micropayment purchases. For example, WeChat
Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as
micropayments.  Different from a typical payment procedure, when micropayments
are made, confirmations can be applied automatically without clients'
permission which aims to provide convenience to both merchant and client.  If a
victim's payment code is leaked to the attackers, they can use that code to
authorize multiple micropayments without needing permission.  In order to prevent such
cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} have designed a refreshing mechanism for the
payment code, which is to refresh the QR code every minute. This is sufficient
to stop an attack like sneak shots but unable to stop a real-time attack like our
\tool.  In summary, the payment QR code is highly sensitive on users' devices
and our following case study is about how to obtain this code using an
attacker-crafted power bank via \tool.

@@

In this part, we will introduce a real-life attack scenario to show that our
\tool is a practical offensive tool.  This scenario can be decomposed into the
following steps.

@@

Next, we summarize the possible threats toward users under different modes.
\hongyi{Better way to express this?}
First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices. Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

@@

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we disclose to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
After each experiment, the raw video and the corresponding \ac{OCR} result file will be generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks. It protects their privacy and is also a mark for us to confirm that the data we find contains their private data. At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} result for us. 
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

@@

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
In total, there are 94,058 entries of data collected among 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expression are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.

>>>>

\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone, the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
%\fengwei{I think it is necessary to explain them in the text again.}

@@

\subsection{Attack Initialization}
After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
\begin{itemize}
	\item \textbf{Screen Mirror}:
		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default. In this case, \tool will inject a sequence of keystrokes and mouse movements to set the victim's device into mirror their screen. For example, in Windows 10, \tool can inject `Win+P' keystroke and a mouse click on the `Duplicate' option. However, as \tool is unable to obtain the screen during this process, this can only be performed blindly with a possibility of failure.
	\item \textbf{Dismiss Notification}:
		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications are raised: 
		\begin{itemize}
		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen. 
		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
		 \item On iPad Pro (\nth{3} generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
		\end{itemize}
		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movement to dismiss some of these notifications. For example, in the first case, \tool is able to inject a sequence of mouse movements to set the screen at mirror mode to dismiss the pop-up.
\end{itemize}
\begin{comment}
\begin{table*}[]
	\begin{tabular}{|c|c|c|c|}
		\hline
		Device                                                               & Operating System                                                                                         & Notification              & Dismiss Action                                            \\ \hline
		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline
		\multirow{2}{*}{HUAWEI P30 (ELE-AL00)}                               & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}EMUI 11.0.0.135(C00E128R2P5)\\ Android 10 based\end{tabular}} & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Persistent notifications  & N/A                                                       \\ \hline
		\multirow{2}{*}{iPad Pro (3rd generation)}                           & \multirow{2}{*}{iOS 14.4 (Build 18D52)}                                                                  & Status bar indicator      & N/A                                                       \\ \cline{3-4}
		&                                                                                                          & Pop-up (only when locked) & N/A                                                       \\ \hline
	\end{tabular}
	\linebreak
	\caption{Notifications about \tool}
	\label{tab:notification}
\end{table*}
\end{comment}

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC in Windows 10 (OS Build 18363.1379) with two \ac{USB} Type-C interfaces as the
target device. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's devices raise a pop-up window asking victims what mode should new screen be set to. \tool immediately inject a sequence of mouse movement and click to set itself as a mirror to the primary monitor. Thus we have successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attacker real-time feedback which allows attacker to perform more accurate attack.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

\textbf{Sharing Power Bank}.  Sharing power banks provide users with short-term
rental of power banks.  The company deploys power bank stations in the city and
users can rent a power bank from any of the power bank stations, charge their
device on the trip, return the rented power bank to the near stations, and pay
the rental fee.

@@

Not only do sharing power bank provide convenience to users, but it also
brings security issues.  We noticed that most of the power bank stations do not
check the integrity of power banks during the rental process, and users are
hardly cautious to check the power banks when connecting their devices.  An
attacker is able to tamper rented power banks and return them to a power bank
station causing a potential threat to subsequent users.

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that is popular in Asia. Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment information from the video stream.  When the victim viewed text or photos withnt\shuqing{?} is typically performed in the following steps:
\ding{182} The client presents the payment QR code on the mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
By presenting this QR code, the client authorizes the proceeding transaction.
\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

Next, we explain one type of payments called micropayment. A micropayment is pre-determined by the payment
service provider with thresholds in the user agreement. In real-world scenarios, payment service providers use different rules
for micropayment purchases. For example, WeChat
Pay~\cite{Wechat-pay} regards transactions under USD \textdollar 154 as
micropayments.  Different from a typical payment procedure, when micropayments
are made, confirmations can be applied automatically without clients'
permission which aims to provide convenience to both merchant and client.  If a
victim's payment code is leaked to the attackers, they can use that code to
authorize multiple micropayments without needing permission.  In order to prevent such
cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} have designed a refreshing mechanism for the
payment code, which is to refresh the QR code every minute. This is sufficient
to stop an attack like opportunistic theft of QR code but unable to stop a real-time attack like our
\tool.  In summary, the payment QR code is highly sensitive on users' devices
and our following case study is about how to obtain this code using an
attacker-crafted power bank via \tool.

@@

In this part, we will introduce a real-life attack scenario to show that our
\tool is a practical offensive tool.  This scenario can be broken down into the
following steps.

@@

Next, we summarize the possible threats toward users under different modes.
%\hongyi{Better way to express this?}
First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices. Moreover, using video capture mode, once the victims accesses their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

@@

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we discloses to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which is considered as a normal power bank usage time.
To obtain data close to real-life, they were requested to use phones just as they would when normally using the shared power banks.\shuqing{check}
After each experiment, the raw video and the corresponding \ac{OCR} result file will be generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks. It protects their privacy and is also a mark for us to confirm that the data we find contains their private data. At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} result for us. 
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

@@

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
In total, there are 94,058 entries of data collected from 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expression are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.

### 2021-03-10 WOOT/Files/introduction.tex
Intro

The \ac{USB} protocol has become popular worldwide
since its appearance, as it provides a unified and easy-to-use approach for a
extensive range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

On the other side of the coin, the security of \ac{USB} has caused severe problems.
Recent research of all USB specifications indicates that security has not been taken into consideration.~\cite{sok}  There are more than 400
vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
result, many attackers exploit these vulnerabilities and the
\textit{trust-by-default} characteristics of \ac{USB} to conduct attacks, which puts
the privacy and financial security of \ac{USB} users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
are conducted by modifying the device firmware, which will disguise
 as ordinary \ac{USB} devices as other types of devices that are \textit{trust-by-default}
by the hosts.  Typical simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
attackers can pretend themselves as regular users, typing malicious commands to
victim computers, downloading and executing malicious scripts, and copying out
private data from disks.  Such attacks can easily escape from traditional
anti-virus software since it is hard to distinguish them from ordinary \ac{USB}
devices.

@@

In this work, we proposed our approach addressing the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
victim's graphical interface during attacks.  Combining it with the emulation
of traditional \acp{HID} like keyboards and mice, attackers are capable of
performing precise attacks.  We did experiments to verify that \tool could also
bypass some countermeasures for BadUSB since they often rely on interaction
with the graphical interface.  Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers are involved in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

>>>>

The \ac{USB} protocol has become popular worldwide
since its appearance\shuqing{When?}, as it provides a unified and easy-to-use approach for a
extensive range of devices to communicate with each other.  From version 1.0 till
now, \ac{USB} specification has evolved rapidly and offered more and more
functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.

Conversely, the security of \ac{USB} has caused severe problems.
Recent research of all USB specifications indicates that security has not been taken into consideration.~\cite{sok}  There are more than 400
vulnerabilities related to \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
result, many attackers exploit these vulnerabilities and the
\textit{trust-by-default} characteristics of \ac{USB} to conduct attacks, which puts
the privacy and financial security of \ac{USB} users in danger~\cite{sok}.

BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
are conducted by modifying the device firmware, which are disguised
 as ordinary \ac{USB} devices as other types of devices that are \textit{trust-by-default}
by the hosts.  Typically, simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
attackers can pretend to be regular users, typing malicious commands to
victims' computers, downloading and executing malicious scripts, and copying out
private data from disks.  Such attacks can easily \shuqing{arg1} get detected by from traditional
anti-virus software since it is hard to distinguish them from ordinary \ac{USB}
devices.

@@

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
victim's graphical interface during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.  
Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers are involved in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information, demonstrating the \shuqing{importance of our re?}.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}
